---
title: "Global Listening Project"
format: pdf
editor: visual
author:
 - name: Alexander Miles
   affiliations:
     - id: University of Southern California
 - name: Jeremy Miles
   affiliations:
      - id: Google
 - name: GLP Project Team
date: today
echo: false  # Hides code by default for all chunks


---

```{r}

library(dplyr)
library(ggplot2)
library(foreign)

options(dplyr.summarise.inform = FALSE)

setwd("C:\\Users\\jerem\\Downloads") ### FIX

suppressWarnings({
  orig_dat <- foreign::read.spss("Global Listening Project - Final Data.sav", 
                          to.data.frame = TRUE) 
})
```

```{r}


```

```{r}


dat <- orig_dat
names(dat) <- tolower(names(dat)) 
dat <- dat %>% dplyr::mutate(
  global_region = as.character(global_region),
  gender = as.character(gender),
  gender = ifelse(gender %in% c("Male", "Female"), gender, NA),
  youth = age_group == "18-24 years old",
  youth = ifelse(youth, "Age 18-24", "Age25+"),
  Region = as.character(region), 
  country = as.character(country))


```

## Trust in Media for Sources of Information

Imagine there was an emerging crisis in your country that you were very concerned about and
wanted to learn more about (for example, a flood, pandemic, or food/water shortages).
How likely would you be to trust the following sources to give you the most accurate, truthful
information?


```{r}
#| fig-width: 9
#| fig-height: 10

TrustGraphs <- function(varq, var_label) {
  dat$var <- dat[[varq]]
  
  #Create summary by for all countries
  summary_dat <- dat %>% 
    dplyr::filter(var != "Don't know/ Refused") %>%
    dplyr::group_by(var, youth) %>% 
    dplyr::summarise(n = dplyr::n()) %>% 
    dplyr::group_by(youth) %>% 
    dplyr::mutate(tot = sum(n), prop = n / tot) %>%
    dplyr::ungroup()
  
  t1 <- summary_dat %>%
    dplyr::select(var, youth, prop) %>%
    dplyr::mutate(prop = round(prop, 2)) %>%
    tidyr::pivot_wider(
      names_from = youth, values_from = prop
      ) %>%
    dplyr::rename(Likelihood = var)

  names(t1)[[1]] <- var_label
  
  # plot for all countries
  p1 <- summary_dat %>%
    ggplot2::ggplot(aes(x = youth, y = prop, fill = var)) +
    ggplot2::geom_bar(stat = "identity") + 
    ylab(glue::glue("Proportion ", var_label)) +
    xlab("Age Group") + 
    labs(fill = "Likelihood of Trust") +
    ggtitle(glue::glue(var_label, ": all countries")) +
    theme(axis.text.x=element_text(angle=90, hjust=1))
  
  summary_country_dat <- dat %>% 
    dplyr::filter(var != "Don't know/ Refused") %>%
    dplyr::group_by(var, youth, country) %>% 
    dplyr::summarise(n = dplyr::n()) %>% 
    dplyr::group_by(youth, country) %>% 
    dplyr::mutate(tot = sum(n), prop = n / tot) 
  
  
  
  t2 <- summary_country_dat %>%
    dplyr::select(var, youth, prop, country) %>%
    dplyr::mutate(prop = round(prop, 2)) %>%
    tidyr::pivot_wider(
      names_from = youth, values_from = prop
      ) %>%
    dplyr::rename(Likelihood = var) %>%
    dplyr::arrange(country)

  names(t2)[[1]] <- var_label
  
  p2 <- summary_country_dat %>%
    ggplot2::ggplot(aes(x = youth, y = prop, fill = var)) +
    ggplot2::geom_bar(stat = "identity") +
    facet_wrap(~country) + 
    ylab(glue::glue("Proportion ", var_label)) +
    xlab("Age Group") + 
    labs(fill = "Likelihood of Trust") +
    ggtitle(var_label) +
    theme(axis.text.x=element_text(angle=90, hjust=1))
  
  return(list(p1 = p1, p2 = p2, t1 = t1, t2 = t2))
}  

trust_vars <- paste0("a1_", 1:13)
trust_sources <- 
  c("National TV",
    "Local TV",
    "National Radio",
    "Local Radio",
    "International TV",
    "International Radio",
    "National Print Media",
    "Local Print Media",
    "Word of mouth",
    "Govt Communication",
    "Social Media",
    "Internet",
    "Messaging Platforms")

list_graphs <- 
  lapply(1:13, function(x) {
    TrustGraphs(var = trust_vars[[x]], var_label = trust_sources[x])
  })


for(i in 1:length(list_graphs)) {
  list_graphs[[i]]$t1 %>% knitr::kable() %>% print()
  list_graphs[[i]]$p1 %>% print()
  list_graphs[[i]]$t2 %>% 
    dplyr::arrange(country) %>% 
    knitr::kable() %>% print()
  list_graphs[[i]]$p2 %>% print()
  cat('\\newpage')
}


```
## Trust in Individuals

Again, thinking about an emerging crisis in your country that you were very concerned about
and wanted to learn more about (for example, a flood, pandemic, or food/water shortages). Who
would you likely turn to for information?

```{r}
#| fig-width: 9
#| fig-height: 10

rm(trust_vars)
rm(trust_sources)
trust_vars <- paste0("a2_", 1:13)
trust_sources <- 
  c("Family members",
    "Religious leaders",
    "Community leaders",
    "Friends",
    "Social media influencers",
    "Local politicians",
    "Government and political leaders",
    "Local Print Media",
    "Journalists",
    "NGOs / CSOs",
    "International Authorities",
    "Family doctor / healthcare",
    "Scientists")

list_graphs <- lapply(1:13, function(x) {
  TrustGraphs(var = trust_vars[[x]], var_label = trust_sources[x])
})

for(i in 1:length(list_graphs)) {
  list_graphs[[i]]$t1 %>% knitr::kable() %>% print()
  list_graphs[[i]]$p1 %>% print()
  list_graphs[[i]]$t2 %>% 
    dplyr::arrange(country) %>% 
    knitr::kable() %>% print()
  list_graphs[[i]]$p2 %>% print()
  cat('\\newpage')
}


```