---
title: "Mental Health Analysis"
author: "Alex Miles, Jeremy Miles"
format:
  html5:
    fig-height: 20
    fig-width: 15
editor: visual
keep-md: true
execute: 
  cache: true
knitr: 
  opts_chunk:
    R.options:
        knitr.graphics.auto_pdf: true
---

# Looking at Mental, Trust, Optimism and Age

From doc: We can test for a significant difference in the strength of the relationship between mh and trust/optimism across age groups.

```{r setup}
#| echo: false

library(dplyr)
library(foreign)
library(ggplot2)
library(ggrepel)
library(haven)
library(knitr)
library(locfit)

DisplayGgplot <- function(p, width = 3, height = 2) {
  file_name <- paste0(tempfile(), ".png")
  suppressMessages(
    ggplot2::ggsave(filename = file_name,
                    plot = p,
                    width = width,
                    height = height,
                    device = "png",
                    units = "in")
  )
  
  return(file_name)
}

```

```{r fig.height=20,fig.width=15}
#| echo: false



# Download the .sav file from the URL if the file does not exist.
if (!file.exists("Global_Listening_Project_Final_Data.sav")) {
  url <- glue::glue("https://github.com/jeremymiles/glp/blob",
                    "/main/Global%20Listening%20Project%20-", 
                    "%20Final%20Data.sav?raw=true")
  download.file(
    url, 
    destfile = "Global_Listening_Project_Final_Data.sav", mode = "wb")
  
  data_haven <- haven::read_sav("Global_Listening_Project_Final_Data.sav")
  
  # Save the data as a .sav file in a format compatible with foreign
  haven::write_sav(data_haven, "Compatible_Final_Data.sav")
  
}
# Read the .sav file using haven
# Want to use foreign, as it keeps factor labels. Foreign can't read from the 
# url, unclear why. Fix is to load with haven, write sav file, and read
# that with foreign


# Now read the  saved .sav file using foreign
suppressWarnings({
  orig_dat <- 
    foreign::read.spss(
      "Compatible_Final_Data.sav", 
      to.data.frame = TRUE) 
})

# Removing data_haven from R environment
rm(data_haven)


names(orig_dat) <- tolower(names(orig_dat))

```

```{r}


# rename the trust variables

d <- orig_dat %>%
  # ggplot uses alphabetical order, so a number at the 
  # front keeps the order
  dplyr::rename(
    ` 1. national_tv_media_info` = a1_1,
    ` 2. local_tv_media_info` = a1_2,
    ` 3. trust_media_national_radio_media_info` = a1_3,
    ` 4. local_radio_media_info` = a1_4,
    ` 5. international_tv_media_info` = a1_5,
    ` 6. international_radio_media_info` = a1_6,
    ` 7. national_print_media_info` = a1_7,
    ` 8. local_print_media_info` = a1_8,
    ` 9. word_of_mouth_media_info` = a1_9,
    `10. govt_comms_media_info` = a1_10,
    `11. social_media_media_info` = a1_11,
    `12. internet_media_info` = a1_12,
    `13. messaging_media_info` = a1_13,
    # people
    ` 1. family_people_info`            = a2_1,
    ` 2. religious_people_info`         = a2_2,
    ` 3. community_leaders_people_info` = a2_3,
    ` 4. friends_people_info`           = a2_4,
    ` 5. social_medial_people_info`     = a2_5,
    ` 6. local_politician_people_info`  = a2_6,
    ` 7. govt_pol_leaders_people_info`  = a2_7,
    ` 8. journalists_people_info`       = a2_8,
    ` 9. ngos_people_info`              = a2_9,
    `10. int_authority_people_info`     = a2_10,
    `11. employer_colleague_people_info`= a2_11,
    `12. family_doc_people_info`        = a2_12,
    `13. scientist_people_info`         = a2_13,
    # who would you trust to act in your interests?
    `1. government_trust`          = b1_1,
    `2. health_authorities_trust`  = b1_2,
    `3. int_orgs_trust`            = b1_3,
    # 
    ` 1. neighbors_interest`          = b2_1,
    ` 2. scientists_interest`         = b2_2,
    ` 3. celebs_interest`             = b2_3,
    ` 4. religious_interest`          = b2_4,
    ` 5. community_leaders_interest`  = b2_5,
    ` 6. politic_leaders_interest`    = b2_6,
    ` 7. ngos_interest`               = b2_7,
    ` 8. employer_interest`           = b2_8,
    ` 9. family_docs_interest`        = b2_9,
    `10. family_interest`             = b2_10
  ) %>%
  dplyr::mutate(
    mh_problems = ifelse(c1_6 == "Yes", TRUE, ifelse(
      c1_6 == "No", FALSE, NA)),
    lonely = ifelse(c1_1 == "Yes", TRUE, ifelse(
      c1_1 == "No", FALSE, NA))
  ) %>%
  dplyr::mutate_at(
    vars(ends_with("info")), as.numeric
  ) %>%
    dplyr::mutate_at(
    vars(ends_with("trust")), as.numeric
  ) %>%
    dplyr::mutate_at(
    vars(ends_with("interest")), as.numeric
  ) %>%
  # Optimism
  dplyr::mutate(
    financial_optimism = 
      ifelse(as.numeric(d1_1) < 5, as.numeric(d1_1), NA
             ),
    economy_optimism = 
      ifelse(as.numeric(d1_2) < 5, as.numeric(d1_2), NA
             ),
    health_optimism = 
      ifelse(as.numeric(d1_1) < 5, as.numeric(d1_1), NA
             ),
  )



d <- d %>% dplyr::mutate(
  global_region = as.character(global_region),
  gender = as.character(gender),
  gender = ifelse(gender %in% c("Male", "Female"), gender, NA),
  youth = age_group == "18-24 years old",
  youth = ifelse(youth, "Age 18-24", "Age25+"),
  Region = as.character(region), 
  country = as.character(country),
  age_group = as.character(age_group),
  age_group = 
    ifelse(age_group == "Don't know/ Prefer not to say", NA, age_group))

```

```{r}

#| results: asis
RunModels <- function(ending, predictor) {
  
  vars <- d %>% 
    select(ends_with(ending)) %>% 
    names() 
  
  d$predictor <- d[[predictor]]
  
  for (outcome_var in vars) {
    

    cat("\n ====================Current outcome variable: ", outcome_var, "==============\n")
    cat("\n ====================Predictor variable: ", predictor, "==============\n")
    
    d$outcome_var <- d[[outcome_var]]
    
    fit_1 <- lme4::lmer(outcome_var ~ (1|country), data = d, REML = FALSE)
    fit_2 <- lme4::lmer(outcome_var ~ age_group + (1|country), data = d, 
                        REML = FALSE)
    
    cat("\n\n\n==================== Fit 2: Age Group =============
        \n")
    cat("\n ====================Predictor variable: ", predictor, "==============\n")
    summary(fit_2) %>% print()
    
    
    fit_3 <- lme4::lmer(
      outcome_var ~ predictor + age_group + (1|country), data = d, REML = FALSE
    )
    
    cat("\n\n\n==================== Fit 3: Add Predictor =============
        \n")
    summary(fit_3) %>% print()
    
    fit_3a <- lme4::lmer(
      outcome_var ~ predictor + age_group + (age_group|country), data = d, 
      REML = FALSE
    )
    
    cat("\n\n\n==================== Fit 3a: Add Random Slope for Predictor =============
        \n")
    summary(fit_3a) %>% print()
    
    anova(fit_3, fit_3a, test = "LRT")
    
    
    fit_4 <- lme4::lmer(
      outcome_var ~ predictor * age_group + (1|country), data = d, 
      REML = FALSE
    )
    cat("\n\n\n==================== Fit 4: Add Interaction =============
        \n")
    summary(fit_4) %>% print()
    
    cat("\n\n\n==================== Fit 4: LRT to Get P-Value for Interaction =============
        \n")
    anova(fit_3, fit_4, test = "LRT") %>% print()
    
    fit_4a <- lme4::lmer(
      outcome_var ~ predictor * age_group + (age_group|country), data = d, 
      REML = FALSE
    )
    summary(fit_4a) %>% print()
    anova(fit_3a, fit_4a, test = "LRT") %>% print()
    
    
    d_grouped <- d%>% 
      dplyr::filter(!is.na(predictor), !is.na(age_group)) %>%
      dplyr::group_by(country) %>%
      dplyr::mutate(outcome_var_mean = mean(outcome_var, na.rm = TRUE)) %>%
      dplyr::mutate(outcome_var_centered = outcome_var - outcome_var_mean) %>%
      dplyr::group_by(age_group, predictor) %>%
      dplyr::summarise(outcome_var = mean(outcome_var_centered))
    
    p <- d_grouped %>% 
      ggplot2::ggplot(
        aes(x = age_group, y = outcome_var, group = predictor, color = predictor)
      ) + 
      geom_line() +
      ggtitle(outcome_var)  
    
    print(p)
    cat("\n ====================Predictor variable: ", predictor, "==============\n")
    d_grouped %>%
      tidyr::pivot_wider(
        names_from = predictor,
        values_from = outcome_var
      ) %>% knitr::kable() %>% print()
  }
}  
```

# Results for Trust in Media Information and Mental Health Problems.

Question: Who would you trust to give you accurate information about an emerging crisis?

### Note: Higher score = LESS LIKELY to trust.

Generally: Mental health problems are associated with HIGHER trust; loneliness
is associated with HIGHER trust.


## Country Level Summary

```{r}


d %>% dplyr::select(
  country, ends_with("media_info")
) %>%
  dplyr::group_by(country) %>%
  dplyr::summarise_all(
    mean, na.rm = TRUE
  ) %>% knitr::kable(digits = 2)
  

```

Lots of output below. I will try to summarise.

## 1. National TV

35-44 have lower trust than 18-25; 45-54 and 55+ have higher trust than 18-25. 
MH problems are associated with HIGHER trust (by 0.025 points on a 1-4 scale, 
so not very much).

The effect of MH problems on trust does not vary across age groups.
Controlling for loneliness, age effect disappears. Barely statistically 
significant interaction effect of loneliness and age - loneliness not associated
with trust in 55+.


## 2. local_tv_media

45-54 and 55+ have HIGHER trust than 18-25.

MH: There is a change in the relationship across age, which appears to be driven
by 55+ with MH problems having higher trust than those without, 
which is the reverse of other age groups.
Loneliness: Large difference in trust for lonely vs not at up to age 44; 
effect reduces and disappears at 55.

## 3. national_radio_media

35-44, 45-54 and 55+ have lower trust than youth. 
MH problems not associated
with trust (controlling for age group) No variation in MH effect across 
age detected.
Loneliness: consistent difference in trust up to age 55, then effect of 
loneliness disappears. 

## 4. local_radio_media

All age groups have higher trust than youth. 

MH problem effect does not vary across age.
Loneliness effect varies slightly across age - oldest people have lowest effect.

## 5. International TV

35+ have less trust than youth. 
MH: Larger trust gap in youth than older.
Loneliness: Slightly larger in youth, but not statistically significant.

## 6. International Radio

Similar to TV, 35+ have less trust (55+ much less difference). 
MH: Gap is larger in youth than older, but barely statistically significant.
Loneliness: Age-Loneliness effect not (even close to) statistically significant.


## 7. National Print Media

All groups have lower trust than youth. 
MH: No statistically significant 
differences in the effect of MH on trust in different age groups.
Loneliness: Larger trust gap ain younger (<45) age groups.

## 8. Local Print Media

No statistically significant age effect. 
MH: Graph looks like something interesting 
is happening, but appears not significant (possible estimation error though).
Loneliness: Trust gap in lonely vs not shrinks in older age groups.

## 9. Word of Mouth Media

All groups HIGHER trust than youth. Smallest difference with 55+.
MH: Smaller effect of MH in youth than in other age groups.
Loneliness: Also smaller effect of loneliness in younger people. 

## 10. Govt Communications

35+ lower trust than youth. 
MH: No statistically significant effect of MH on the level of trust across 
age groups.
Loneliness: Large effect for youth and up to age 44. Small or reversed effect
for older.


## 11. Social Media

All age groups trust social media LESS than youth (25-34 only slightly, 55+ dramatically).

MH: Effect of MH is consistent across age groups.
Loneliness: Marginally significant effect. Hard to see in the graph. Perhaps
smaller difference for younger people.



## 12. Internet Media

All age groups have significantly lower trust than youth - trust decreases with
age.


Effect of MH is consistent across age groups.
Effect of loneliness is consistent across age.

## 13. Messaging Media

Trust lower in 35+ than youth. 55+ considerably so.

No difference in the effect of MH or loneliness across age groups.

(Sorry, the graphs are not positioned nicely, I can't work out how to make them appear in the right place.)

```{r media_mh}

RunModels(ending = "media_info", predictor = "mh_problems")

```



```{r media_lonely}

RunModels(ending = "media_info", predictor = "lonely")

```

# A2: Which People Would you Trust for Information

## Country Level Summary

### Note: Higher score = LESS TRUST



```{r}


d %>% dplyr::select(
  country, ends_with("people_info")
) %>%
  dplyr::group_by(country) %>%
  dplyr::summarise_all(
    mean, na.rm = TRUE
  ) %>% knitr::kable(digits = 2)
  

```



# A2: Results for Trust in Media Information and Loneliness.

Question: Who would you trust to give you accurate information about an emerging 
crisis?

## 1. Family

No evidence of age effects.
MH associated with more trust in family. No difference in MH trust across age 
groups.



## 2. Religious Leaders

25-44 have slightly more trust in religious leaders than youth. 55+ have less.

MH associated with more trust. No differences found across age.

## 3. Community Leaders

55+ less trust than youth. 
MH associated with more trust. No variation in the effect across age.

## 4. Friends

35-54 have more trust than yout. 25-34 and 55+ no differences seen.

MH associated with less trust in friends. No evidence of age effect.

## 5. Social Media

Older people have less trust - amount decreases more as groups get older.
MH problems associated with more trust. Age effect on difference is statistically
significant, but a bit weird - effect of MH on trust is larger in 35-44 and 
45-54 year olds than other groups. 

## 6. Local politicians

Trust decreases with older people. 
MH problems predict greater trust. No age effect in the difference.

## 7. Govt and political leaders

All age groups trust less than youth. 
MH predicts more trust. Larger trust gap for middle age groups than youth 
and 55+.

## 8. Journalists.

Older groups trust less than youth.

MH problems associated with more trust. No difference in effect across age.

## 9. NGOs

Older people have less trust in NGOs. 
MH problems associated with less trust. No interaction effect.

## 10. International Authorities

Older people have lower trust. 

MH problems associated with higher trust. No significant difference in MH 
problems across age groups. 

## 11. Employer and colleagues

25-54 trust employer and colleagues more than youth, 55+ trust less than youth. 

MH problems associated with more trust.  No interaction effect with age. 

## 12. Family doctor or healthcare provides.

Older ages trust their doctor more than youth (more when 55+).
MH problems associated with more trust. No interaction effect with age.

## 13. Scientists.

Older age associated with less trust.

Mental health associated with more trust. This gap shrinks in older age groups.















```{r info_mh}

RunModels(ending = "people_info", predictor = "mh_problems")

```



```{r info_lonely}

RunModels(ending = "people_info", predictor = "lonely")

```

# Which Organizations Would you Trust to act in your interests:

### Higher score = LESS TRUST

```{r}


d %>% dplyr::select(
  country, ends_with("trust")
) %>%
  dplyr::group_by(country) %>%
  dplyr::summarise_all(
    mean, na.rm = TRUE
  ) %>% knitr::kable(digits = 2)

```

## Mental Health

```{r trust_mh}

RunModels(ending = "trust", predictor = "mh_problems")

```

# Which Organizations Would you Trust to act in your interests: Mental Health

```{r trust_lonely}

RunModels(ending = "trust", predictor = "lonely")

```

# Optimism

### Note: Lower score = more optimistic

```{r optimism}

d %>% dplyr::select(
  country, ends_with("optimism")
) %>%
  dplyr::group_by(country) %>%
  dplyr::summarise_all(
    mean, na.rm = TRUE
  ) %>% knitr::kable(digits = 2)
```
