---
title: "Mental Health Analysis"
author: "Alex Miles, Jeremy Miles"
format: html
editor: visual
---

# Looking at Mental, Trust, Optimism and Age

From doc: We can test for a significant difference in the strength of the relationship between mh and trust/optimism across age groups.





```{r setup}
#| echo: false

library(dplyr)
library(foreign)
library(ggplot2)
library(ggrepel)
library(haven)
library(locfit)

```

```{r fig.height=20,fig.width=15}
#| echo: false
#| cache: true


# Download the .sav file from the URL if the file does not exist.
if (!file.exists("Global_Listening_Project_Final_Data.sav")) {
  url <- glue::glue("https://github.com/jeremymiles/glp/blob",
                    "/main/Global%20Listening%20Project%20-", 
                    "%20Final%20Data.sav?raw=true")
  download.file(
    url, 
    destfile = "Global_Listening_Project_Final_Data.sav", mode = "wb")
  
  data_haven <- haven::read_sav("Global_Listening_Project_Final_Data.sav")
  
  # Save the data as a .sav file in a format compatible with foreign
  haven::write_sav(data_haven, "Compatible_Final_Data.sav")
  
}
# Read the .sav file using haven
# Want to use foreign, as it keeps factor labels. Foreign can't read from the 
# url, unclear why. Fix is to load with haven, write sav file, and read
# that with foreign


# Now read the  saved .sav file using foreign
suppressWarnings({
  orig_dat <- foreign::read.spss("Compatible_Final_Data.sav", 
                                 to.data.frame = TRUE) 
})

# Removing data_haven from R environment
rm(data_haven)


names(orig_dat) <- tolower(names(orig_dat))

```



```{r fig.height=20,fig.width=15}


# rename the trust variables

d <- orig_dat %>%
  # ggplot uses alphabetical order, so a number at the 
  # front keeps the order
  dplyr::rename(
    ` 1. national_tv_media` = a1_1,
    ` 2. local_tv_media` = a1_2,
    ` 3. trust_media_national_radio_media` = a1_3,
    ` 4. local_radio_media` = a1_4,
    ` 5. international_tv_media` = a1_5,
    ` 6. international_radio_media` = a1_6,
    ` 7. national_print_media` = a1_7,
    ` 8. local_print_media` = a1_8,
    ` 9. word_of_mouth_media` = a1_9,
    `10. govt_comms_media` = a1_10,
    `11. social_media_media` = a1_11,
    `12. internet_media` = a1_12,
    `13. messaging_media` = a1_13) %>%
  dplyr::mutate(
    mh_problems = ifelse(c1_6 == "Yes", TRUE, ifelse(
      c1_6 == "No", FALSE, NA))
  ) %>%
  dplyr::mutate_at(
    vars(ends_with("media")), as.numeric
  )


d <- d %>% dplyr::mutate(
  global_region = as.character(global_region),
  gender = as.character(gender),
  gender = ifelse(gender %in% c("Male", "Female"), gender, NA),
  youth = age_group == "18-24 years old",
  youth = ifelse(youth, "Age 18-24", "Age25+"),
  Region = as.character(region), 
  country = as.character(country),
  age_group = as.character(age_group),
  age_group = ifelse(age_group == "Don't know/ Prefer not to say", NA, age_group))

```

# Results

Lots of output below. I will try to summarise.

##1. National TV 

35-44 have higher trust than 18-25, 45-54 and 55+ have lower trust than 18-25.
MH problems are associated with lower trust (by 0.025 points on a 1-4 scale, so 
not very much).

The effect of MH problems on trust does not vary across age groups.

## 2. local_tv_media
45-54 and 55+ have lower trust than 18-25.

There is a change in the relationship across age, which appears to be driven by
55+ with MH  problems having higher trust than those without, which is the 
reverse of other age groups.

## 3. national_radio_media

35-44, 45-54 and 55+ have lower trust than youth.
MH problems not associated with trust (controlling for age group)
No variation in MH effect across age detected.

## 4. local_radio_media

All age groups have lower trust than youth.

MH problem effect does not vary.


```{r}

vars <- d %>% 
  select(ends_with("media")) %>% 
  names() 


for (outcome_var in vars) {
  
  cat("Current outcome variable: ", outcome_var, "\n")
  
  d$outcome_var <- d[[outcome_var]]
  
  fit_1 <- lme4::lmer(outcome_var ~ (1|country), data = d, REML = FALSE)
  fit_2 <- lme4::lmer(outcome_var ~ age_group + (1|country), data = d, 
                      REML = FALSE)
  summary(fit_2) %>% print()
  fit_3 <- lme4::lmer(
    outcome_var ~ mh_problems + age_group + (1|country), data = d, REML = FALSE
  )
  summary(fit_3) %>% print()
  
  fit_3a <- lme4::lmer(
    outcome_var ~ mh_problems + age_group + (age_group|country), data = d, 
    REML = FALSE
  )
  summary(fit_3a) %>% print()
  
  anova(fit_3, fit_3a, test = "LRT")
  
  
  fit_4 <- lme4::lmer(
    outcome_var ~ mh_problems * age_group + (1|country), data = d, 
    REML = FALSE
  )
  summary(fit_4) %>% print()
  anova(fit_3, fit_4, test = "LRT") %>% print()
  
  fit_4a <- lme4::lmer(
    outcome_var ~ mh_problems * age_group + (age_group|country), data = d, 
    REML = FALSE
  )
  summary(fit_4a) %>% print()
  anova(fit_3a, fit_4a, test = "LRT") %>% print()
  
  
  d_grouped <- d%>% 
    dplyr::filter(!is.na(mh_problems), !is.na(age_group)) %>%
    dplyr::group_by(country) %>%
    dplyr::mutate(outcome_var_mean = mean(outcome_var, na.rm = TRUE)) %>%
    dplyr::mutate(outcome_var_centered = outcome_var - outcome_var_mean) %>%
    dplyr::group_by(age_group, mh_problems) %>%
    dplyr::summarise(outcome_var = mean(outcome_var_centered))
  
  p <- d_grouped %>% 
    ggplot2::ggplot(
      aes(x = age_group, y = outcome_var, group = mh_problems, color = mh_problems)
    ) + 
    geom_line() +
    ggtitle(outcome_var)  
  print(p)
}


```
